No need to know: astrophysics-agnostic gravitational wave cosmology

### 2024-03-26 src/tex/ms.tex
[showyourwork] overleaf sync

The code used to generate all simulated data, perform the population inference, and create all figures in this paper is made publicly available at \GitHubURL{githubLink}, and was enabled by the \showyourwork package \citep{Luger2021}.

>>>>

The code used to generate all simulated data, perform the population inference, and create all figures in this paper is made publicly available at \GitHubURL{}, and was enabled by the \showyourwork package \citep{Luger2021}.
